---
<<<<<<< HEAD
title: "RR Peer Assessment 1"
author: "Sunil"
date: "Thursday, March 12, 2015"
output: html_document
---
Loading and preprocessing the data

```{r}
activity <- read.csv("C:/Users/Sunil/Google Drive/upload/activity.csv", colClasses = c("numeric", "character","numeric"))

head(activity)

names(activity)

library(lattice)

activity$date <- as.Date(activity$date, "%Y-%m-%d")
```

What is mean total number of steps taken per day?

a)Calculate the total number of steps taken per day

```{r}
stepsTotal <- aggregate(steps ~ date, data = activity, sum, na.rm = TRUE)
```

b)Histogram of the total number of steps taken each day

```{r, echo=TRUE}
hist(stepsTotal$steps, main = "total steps taken per day", xlab = "day", col = "red")
```

c)The mean and median of the total number of steps taken per day

```{r}
mean(stepsTotal$steps)

median(stepsTotal$steps)
```

What is the average daily activity pattern?

```{r}
timeSeries <- tapply(activity$steps, activity$interval, mean, na.rm = TRUE)
```

a)Time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)

```{r, echo=TRUE}
plot(row.names(timeSeries), timeSeries, type = "l", xlab = "5 minute interval", 
     ylab = "averaged across all days", main = "average number of steps taken", 
     col = "red")

```

b)5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?

```{r}

maxInterval <- which.max(timeSeries)

names(maxInterval)
```

Inputing missing values

```{r}

activityNA <- sum(is.na(activity))
```

The total number of missing values in the dataset (i.e. the total number of rows with NAs)

```{r}
activityNA
```

Filling in all of the missing values in the dataset. 

```{r}
stepsAverage <- aggregate(steps ~ interval, data = activity, FUN = mean)

fillNA <- numeric()

for (i in 1:nrow(activity)) 
  {
  obs <- activity[i, ]
  if (is.na(obs$steps)) 
    {
    steps <- subset(stepsAverage, interval == obs$interval)$steps
    } else 
           {
           steps <- obs$steps
           }
  fillNA <- c(fillNA, steps)
}

newActivity <- activity
newActivity$steps <- fillNA
```

New dataset that is equal to the original dataset but with the missing data filled in.

```{r}
stepsTotal2 <- aggregate(steps ~ date, data = newActivity, sum, na.rm = TRUE)
```

Histogram of the total number of steps taken each day

```{r, echo=TRUE}
hist(stepsTotal2$steps, main = "total steps taken per day", xlab = "day", col = "red")

```

The mean and median total number of steps taken per day.

```{r}
mean(stepsTotal2$steps)

median(stepsTotal2$steps)
```

Result: They are the same

Are there differences in activity patterns between weekdays and weekends?

```{r}
day <- weekdays(activity$date)
daylevel <- vector()
for (i in 1:nrow(activity)) 
  {
  if (day[i] == "Saturday") 
    {
    daylevel[i] <- "Weekend"
    } else if (day[i] == "Sunday") 
          {
          daylevel[i] <- "Weekend"
          } else 
                {
                daylevel[i] <- "Weekday"
  }
}
activity$daylevel <- daylevel
activity$daylevel <- factor(activity$daylevel)

stepsPerDay <- aggregate(steps ~ interval + daylevel, data = activity, mean)
names(stepsPerDay) <- c("interval", "daylevel", "steps")
```

Panel plot containing a time series plot 

```{r, echo=TRUE}
xyplot(steps ~ interval | daylevel, stepsPerDay, type = "l", layout = c(1, 2), xlab = "Interval", 
       ylab = "Number of steps")

```
=======
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data



## What is mean total number of steps taken per day?



## What is the average daily activity pattern?



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
>>>>>>> 80edf39c3bb508fee88e3394542f967dd3fd3270
